Activity Recognition with mobile devices\\

### 2018-05-25 paper/main.tex
Introduction

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[printonlyused]{acronym}
\usepackage{graphicx}
\usepackage{textcomp}
%\usepackage[backend=bibtex,style=IEEEtr]{biblatex}

@@

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
TODO
\end{abstract}

@@

\section{Introduction -- Simon}
asdfas
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
intro

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage[printonlyused]{acronym}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{color}
%\usepackage[backend=bibtex,style=IEEEtr]{biblatex}

@@

\begin{abstract}
This document is a discussion on the topic activity recognition focusing on \ac{HAR} using mobile device accelerometers. Existing studies and papers are therefore examined and the different approaches of data collecting and processing are illustrated. For this work no separate experiments were carried out. However advantages and disadvantages of existing studies like activity recognition using a single tri-axial accelerator or using a set of multiple accelerators placed on different parts of the body are compared. What's more also current as well as future possibilities of \ac{HAR} concerning the health and sports sector are reflected. As pattern detection of different human gestures is a complex task, we concentrate on just on some main activities like walking, jogging, sitting, standing, ascending stairs and descending stairs. The goal is to point out aspects that apply to the majority of world's population and their most common everyday activities. Furthermore gesture detection involves processing power which is limited on mobile devices and also battery draining. Methods like configuring sampling rate in this way help saving power and optimizing the activity recognition task.
\color{red}{*CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.}
\end{abstract}

@@

\section{Introduction -- Simon}
Epic intro
